% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2014 Todd C. Miller <Todd.Miller@sudo.ws> http://www.sudo.ws/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\usepackage[normalem]{ulem}
\usepackage{enumitem}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{hyperref}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
%\newcommand{\labelenumi}{\arabic
%\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resheading}[1]{{{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.3in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}}

%-----------------------------------------------------------
\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Timothy James Barrett}  & Email : timothy@jamesbarrett.us\\
https://github.com/tjbarrett42 &  Mobile : +1-973-830-7907\\
& Website : https://jamesbarrett.us
\end{tabular*}
\vspace{-0.2in}

\resheading{\hspace{0em}\uline{\textsc{EDUCATION}\hfill}}
\vspace{-0.2in}
\begin{itemize}[leftmargin=*]
	
\item
	\ressubheading{Stevens Institute of Technology}{Hoboken, NJ}{Bachelor of Science in Computer Science}{Sep. 2016 - May 2020}

\end{itemize}
\vspace{-0.05in}

\resheading{\hspace{0em}\uline{\textsc{WORK EXPERIENCE}\hfill}}
\vspace{-0.2in}
\begin{itemize}[leftmargin=*]
\item
	\ressubheading{Allvue Systems}{New York, NY}{Application Engineer, Operations}{July 2020 - Present}
	\vspace{-0.1in}
	\begin{itemize}[leftmargin=*]
	\setlength\itemsep{0em}
		\item{Implemented Salesforce database searching for proprietary Chrome extension increasing documentation cross-referencing productivity for 30 engineers.}
		\item{Delivered SQL scripts for client production environments to resolve trade data inconsistencies with back office providers.}
		\item{Documented client implementation defects and translated to consulting requests.}
		\item{Managed product expectations and functionality for client base of over 50 different hedge funds, firms, and investment banks through email and phone.}
	\end{itemize}
	
\item
	\ressubheading{New Jersey Innovation Institute}{Newark, NJ}{Project Assistant and Consultant, Innovation Services}{June 2019 - Aug. 2019}
	\vspace{-0.1in}
	\begin{itemize}[leftmargin=*]
	\setlength\itemsep{0em}
		\item{Created the project prioritization system for incubation of high ROI solutions within physician networks, securing a \$1,000,000 contract.}
		\item{Negotiated directly with client executives to ensure operation within project budgets.}
		
	\end{itemize}

\end{itemize}

\resheading{\hspace{0em}\uline{\textsc{PROJECTS}\hfill}}
\vspace{-0.25in}

\begin{itemize}[leftmargin=*]
\item
	\ressubheading{Workout Split Planner \href{https://exercise-planner.vercel.app}{(exercise-planner.vercel.app)}}{Haledon, NJ}{Personal}{January 2022}
	\vspace{-0.1in}
	\begin{itemize}[leftmargin=*]
	\setlength\itemsep{0em}
		\item{Deployed and managing a React interactive workout routine builder designed for optimizing and visualizing weekly volume and timing with over 1300 exercises from the  ExerciseDB API.}
		\item{Modified the drag-and-drop library react-beautiful-dnd into controlled components to manipulate all states using hooks.}
		\item{Utilized memoization to reduce render lag during client-side state updates.}
		\item{Visualized aggregated planner data using responsive composed graphs from the recharts library.}
	\end{itemize}
	
\item
	\ressubheading{Total Daily Expenditure Estimator \href{https://tdee-calculator.vercel.app}{(tdee-calculator.vercel.app)}}{Haledon, NJ}{Personal}{January 2022}
	\vspace{-0.1in}
	\begin{itemize}[leftmargin=*]
	\setlength\itemsep{0em}
		\item{Deployed a component-based React webapp for calculating caloric intake requirements based on human measurements using the Mifflin St-Jeor formula.}
		\item{Utilized nested component mapping to efficiently list tables of macronutrient  splits (protein, carbs, fat) for weight maintenance, loss, and gain.}
		\item{Worked with a base of over a dozen current users to implement new features and increase accuracy.}
	\end{itemize}
	
\item
	\ressubheading{Stevens Shuttle System}{Hoboken, NJ}{Student}{August 2019 - May 2020}
	\vspace{-0.1in}
	\begin{itemize}[leftmargin=*]
	\setlength\itemsep{0em}
		\item{Collaborated with students on Senior Design Project to create a user-friendly bus schedule application, increasing arrival time accuracy from 20 to 98 percent.}
		\item{Exercised AWS Lambda operations to compile raw location data from third party bus API.}
		\item{Utilized unsupervised machine learning to group bus data and predict arrivals within 2 minutes.}
		\item{Built a responsive React application to display predicted schedules for student use on both mobile and desktop devices.}
	\end{itemize}
	
\end{itemize}

\resheading{\hspace{0em}\uline{\textsc{TECHNICAL SKILLS}\hfill}}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Languages}  & JavaScript, Python, TypeScript, SQL, C\#, XSLT, Apex (Salesforce)\\
\textbf{\large Technologies \& Libraries}  & React, Redux, Node.js, Express, .NET Framework, HTML, CSS, AWS Lambda\\
\textbf{\large Tools}  & SQL Server Management Studio, Webstorm, Visual Studio, Git, TortoiseSVN\\
\textbf{\large Databases}  & MySQL, MongoDB, Firebase Realtime DB\\
\end{tabular*}

\end{document}