\documentclass[letterpaper,10pt]{article}
\usepackage[normalem]{ulem}
\usepackage{enumitem}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{hyperref}
\usepackage{setspace}

\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resheading}[1]{{{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.3in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}}

%-----------------------------------------------------------
\begin{document}

\begin{spacing}{1.05}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Timothy James Barrett}  & Email : timothy@jamesbarrett.us\\
\href{https://github.com/tjbarrett42}{github.com/tjbarrett42} &  Mobile : +1-973-830-7907\\
& LinkedIn : \href{https://www.linkedin.com/in/timjbarrett/}{linkedin.com/in/timjbarrett}
\end{tabular*}
\vspace{-0in}

\resheading{\hspace{0em}\uline{\textsc{WORK EXPERIENCE}\hfill}}
\vspace{-0.15in}
\begin{itemize}[leftmargin=*]
\item[\raisebox{0.5\baselineskip}{\textbullet}]
	\ressubheading{Haven Technologies}{New York, NY}{Fullstack Software Engineer}{June 2022 - August 2023}
	\vspace{-0.08in}
	\begin{itemize}[leftmargin=*]
	\setlength\itemsep{0.0em}
            \item{Redesigned and rebuilt an insurance policy viewer into a scalable SaaS product using Angular, PostgreSQL, Node.js, and Express, with test coverage via Mocha, Chai, and Sinon.}
		\item{Implemented NgRx for state management and centralized API call patterns, improving consistency and debuggability across the frontend codebase.}
            \item{Led weekly sprint planning and reviews, coordinating delivery timelines and priorities across cross-functional teams.}
            \item{Collaborated on new features from requirements through deployment, contributing to UX design, effort estimation, and implementation.}
	\end{itemize}
\item[\raisebox{0.5\baselineskip}{\textbullet}]
	\ressubheading{Allvue Systems}{New York, NY}{Application Engineer, Operations}{July 2020 - May 2022}
	\vspace{-0.08in}
	\begin{itemize}[leftmargin=*]
	\setlength\itemsep{0.0em}
		\item{Resolved TSQL, XML, and XSLT errors in custom portfolio management software, improving reliability for B2B clients.}
		\item{Wrote scripts to fix trade data and payment processing inconsistencies, ensuring accuracy in compliance assessments.}
		\item{Built Salesforce search tooling with Python to streamline internal ticket prioritization workflows.}
	\end{itemize}
	
\end{itemize}
\vspace{-0.0in}

\resheading{\hspace{0em}\uline{\textsc{PROJECTS}\hfill}}
\vspace{-0.15in}

\begin{itemize}[leftmargin=*]

\item[\raisebox{0.5\baselineskip}{\textbullet}]
	\begin{tabular*}{7.3in}{l@{\extracolsep{\fill}}r}
		\textbf{No Plastic, No Problem.} \textnormal{--- \href{https://noplasticnoproblem.com}{noplasticnoproblem.com}} & 2023--Present \\
		{\small\textit{Next.js, React, TypeScript, Tailwind, Sanity CMS, n8n, Claude API, PostHog, Sentry, Supabase, Vercel}} \\[0.1in]
	\end{tabular*}
	\vspace{0.0in}
	\parbox{\linewidth}{Production affiliate content platform in the sustainability space, serving 10,000+ monthly users with 50+ brand partnerships across the plastic-free consumer goods market.}
	\vspace{-0.1in}
	\begin{itemize}[leftmargin=*]
	\setlength\itemsep{0.0em}
		\item{Built and operate a production affiliate platform serving 10,000+ monthly users, with a custom TypeScript/Sanity pipeline managing 200+ content entities and a bidirectional Notion integration powering the full editorial workflow.}
		\item{Built an end-to-end content automation pipeline using n8n, DataForSEO, and the Claude API, cutting SEO brief generation from hours of manual research to fully automated output and supporting a 3x increase in content throughput.}
		\item{Reduced CDN request volume by 85\% and eliminated compute cost spikes by migrating to webhook-driven ISR revalidation, with automated search index regeneration triggered on every content publish.}
		\item{Raised mobile PageSpeed scores from the mid-50s to the mid-80s by resolving LCP and CLS issues, including image optimization, lazy loading, and layout stability fixes across the site.}
		\item{Instrumented PostHog across the affiliate funnel to track click-through behavior and conversion patterns, informing content placement and brand partnership decisions.}
		\item{Built a keyword ranking tracker in Supabase backed by DataForSEO, surfacing historical position trends and cannibalization signals to guide content prioritization and gap strategy.}
		\item{Built a custom MCP server connecting Sanity and Notion as a live knowledge graph, giving AI workflows real-time access to article inventory and brand relationships for fully grounded content generation.}
	\end{itemize}

\end{itemize}

\resheading{\hspace{0em}\uline{\textsc{EDUCATION}\hfill}}
\vspace{-0.15in}
\begin{itemize}[leftmargin=*]
\item[\raisebox{0.5\baselineskip}{\textbullet}]
	\ressubheading{Stevens Institute of Technology}{Hoboken, NJ}{Bachelor of Science in Computer Science}{September 2016 - May 2020}

\end{itemize}
\vspace{-0.0in}

\resheading{\hspace{0em}\uline{\textsc{TECHNICAL SKILLS}\hfill}}
\vspace{-0.1in}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{Programming}  & TypeScript, JavaScript, HTML/CSS, Python3, Java, SQL \\
\textbf{Frameworks \& Libs.}  & Angular, React, Redux, Next.js, NgRx, RxJS, Express, Node.js, Tailwind CSS \\
\textbf{Tools}  & VSCode, Git, GitHub, Vercel, Sanity, n8n, Sentry, PostHog, Vitest, Docker, Postman, Jira, AWS \\
\textbf{Databases}  & MongoDB, PostgreSQL, Supabase, Oracle, MySQL \\
\end{tabular*}

\end{spacing}

\end{document}