% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2014 Todd C. Miller <Todd.Miller@sudo.ws> http://www.sudo.ws/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\usepackage[normalem]{ulem}
\usepackage{enumitem}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{hyperref}
\usepackage{setspace}

\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
%\newcommand{\labelenumi}{\arabic
%\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resheading}[1]{{{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.3in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}}

%-----------------------------------------------------------
\begin{document}

\begin{spacing}{1.2}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Timothy James Barrett}  & Email : timothy@jamesbarrett.us\\
\href{https://jamesbarrett.us}{jamesbarrett.us} &  Mobile : +1-973-830-7907\\
\href{https://github.com/tjbarrett42}{github.com/tjbarrett42} & LinkedIn : \href{https://www.linkedin.com/in/timjbarrett/}{linkedin.com/in/timjbarrett}
\end{tabular*}
\vspace{-0in}



\resheading{\hspace{0em}\uline{\textsc{WORK EXPERIENCE}\hfill}}
\vspace{-0.2in}
\begin{itemize}[leftmargin=*]
\item[\raisebox{0.5\baselineskip}{\textbullet}]
	\ressubheading{Haven Technologies}{New York, NY}{Fullstack Software Engineer}{June 2022 - August 2023}
	\vspace{-0.05in}
	\begin{itemize}[leftmargin=*]
	\setlength\itemsep{0.1em}
            \item{Redesigned and rebuilt outdated insurance policy viewer into a scalable and modern SaaS solution using Angular, PostgreSQL, Node.js, and Express.}
		\item{Implemented NgRX for state management, centralizing API calls and ensuring consistent data flow resulting in a more maintainable and debug-friendly system.}
            \item{Coordinated weekly sprint planning and reviews, translating the timing and priority of sprint deliverables with cross-functional teams, ensuring alignment with overarching project goals.}
            \item{Directed development of new features from conception to deployment, gathering requirements, drafting UX/UI designs, estimating efforts, and managing user stories.}
	\end{itemize}
\item[\raisebox{0.5\baselineskip}{\textbullet}]
	\ressubheading{Allvue Systems}{New York, NY}{Application Engineer, Operations}{July 2020 - May 2022}
	\vspace{-0.05in}
	\begin{itemize}[leftmargin=*]
	\setlength\itemsep{0.1em}
		\item{Resolved errors in SQL procs, XML data, and XSLT configs with XPath and SQL debugging queries.}
		\item{Designed scripts to resolve trade and B2B data inconsistencies in client production environments.}
		\item{Improved ticket prioritization process by implementing Salesforce database searching functionality.}
	\end{itemize}
	
\end{itemize}
\vspace{-0.0in}

\resheading{\hspace{0em}\uline{\textsc{PROJECTS}\hfill}}
\vspace{-0.2in}

\begin{itemize}[leftmargin=*]

\item[\raisebox{0.5\baselineskip}{\textbullet}]
	\ressubheading{FindMyForecast \href{https://findmyforecast.vercel.app}{(findmyforecast.vercel.app)}}{Haledon, NJ}{Angular, Express, Node.js, MongoDB, RxJS, Google-Auth-Library}{September 2023}
	\vspace{-0.05in}
	\begin{itemize}[leftmargin=*]
	\setlength\itemsep{0.1em}
		\item{Developed a web app for pinpointing favorable weather intersections based on user-defined preferences.}
		\item{Implemented Leaflet.js and caching to seamlessly render dynamic maps from OpenMeteo API data.}
		\item{Integrated Google Sign-In and authentication, enabling users to save weather preferences in MongoDB.}
            \item{Setup automatic production deployment pipeline through Vercel and backend hosting with Heroku.}
	\end{itemize}

\item[\raisebox{0.5\baselineskip}{\textbullet}]
	\ressubheading{ExerciseShare \href{https://exercise-share.vercel.app}{(exercise-share.vercel.app)}}{Haledon, NJ}{React, Redux, Express, MongoDB, Node.js, Material UI, JSON Web Token (JWT)}{March 2022}
	\vspace{-0.05in}
	\begin{itemize}[leftmargin=*]
	\setlength\itemsep{0.1em}
		\item{Built an fullstack exercise sharing website utilizing Redux to manage state between server and client for creating, editing, and commenting on posts.}
		\item{Implemented JSON Web Token Auth and Google OAuth 2.0 for secure user sign-in. }
		\item{Created search and recommendation system to both manually and automatically curate posts for users.}
		
	\end{itemize}
	
\end{itemize}

\resheading{\hspace{0em}\uline{\textsc{EDUCATION}\hfill}}
\vspace{-0.2in}
\begin{itemize}[leftmargin=*]
\item[\raisebox{0.5\baselineskip}{\textbullet}]
	\ressubheading{Stevens Institute of Technology}{Hoboken, NJ}{Bachelor of Science in Computer Science}{September 2016 - May 2020}

\end{itemize}
\vspace{-0.0in}

\resheading{\hspace{0em}\uline{\textsc{TECHNICAL SKILLS}\hfill}}
\vspace{-0.1in}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Programming}  & TypeScript, JavaScript, HTML/CSS, Python, C++, SQL \\
\textbf{\large Frameworks \& Libraries}  & Angular, React, Redux, NgRx, RxJS, Express, Node.js, HTML, CSS \\
\textbf{\large Tools}  & Webstorm, VSCode, Linux, Gitlab, Docker, Kubernetes, AWS, Confluence, Jira \\
\textbf{\large Databases}  & MongoDB, PostgreSQL, MySQL \\
\end{tabular*}

\end{spacing}

\end{document}